### 2017-02-11 README.Rmd
Update README.Rmd

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.13131.svg)](http://dx.doi.org/10.5281/zenodo.13131)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)

>>>>

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.13131.svg)](http://dx.doi.org/10.5281/zenodo.13131)
[![codecov](https://codecov.io/gh/ropensci/RNeXML/branch/master/graph/badge.svg?branch=master)](https://codecov.io/gh/ropensci/RNeXML?branch=master)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)
